\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-08-22 paper.tex
fix in author list

%for single author (just remove % characters)
\author{
{\rm Pantazis Deligiannis$^1$, John Erickson$^2$, Cheng Huang$^3$, Akash Lal$^3$}\\
{\rm Matt McCutchen$^4$, Shaz Qadeer$^3$, Wolfram Schulte$^2$, Paul Thomson$^1$}\\\\
$^1$Imperial College London, $^2$Microsoft, $^3$Microsoft Research, $^4$MIT
} % end author

>>>>

%for single author (just remove % characters)
\author{
{\rm Pantazis Deligiannis$^1$, John Erickson$^2$, Cheng Huang$^3$, Akash Lal$^3$}\\
{\rm Matt McCutchen$^4$, Shaz Qadeer$^3$, Wolfram Schulte$^2$, Paul Thomson$^1$}\\\\
$^1$Imperial College London, $^2$Microsoft, $^3$Microsoft Research\\
$^4$Massachusetts Institute of Technology\\
} % end author
